### 2018-10-19 manuscript.rmd
finishing first species name pass re #5

# These are candidates for renaming
Dtaxa %>% filter(taxon1!=taxon2) %>% arrange( desc(count))

>>>>

# Top of this list are candidates for renaming because they are very similar but have different names
Dtaxa %>% filter(taxon1!=taxon2) %>% arrange( desc(count))

# Top of this list are candidates for renaming because they are very different but have same names

Dtaxa %>% filter(taxon1==taxon2) %>% arrange( count )

taxonomy_reference = read_tsv("taxonomy_info/taxon_table.tsv")
